---
title: "Programming Background"
author: "Jeremias Endrina"
date: "9/6/2021"
---

## My Thoughts on R

I started my masters program at NC State taking ST555 where I learn how to use SAS in gathering, processing, analyzing and presenting data. Unfortunately, I have never used SAS again in any of succeeding courses. Instead, I used R extensively as it is the required software in all of my classes. I had a hard time in most of my classes for I don't know how to use R at that time. I have to spend extra time everyday to learn the basic of it and be successful in those courses. Now, in my last semester of the program, I am taking ST558 Data Science for Statisticians to formalize what I learned about R. I am also enrolled in a Python class which has lots of similarities to R in terms of concepts and syntax. 

Based on my experiences, I can say that R has better packages and functions which are easier to learn. It has packages that are constantly being improved. Another is the R Markdown which makes presentation of results nicer and easier to reproduce. Thanks to the people behind the program who willingly devote their time to make R better.

## Example R Markdown Output
```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path = "../images/")
```

```{r boxplot, message=FALSE, warning=FALSE, include=FALSE}
library(ggplot2)

box <- ggplot(data=iris, aes(x=Species, y=Sepal.Length))
box + geom_boxplot(aes(fill=Species)) + 
  ylab("Sepal Length") + ggtitle("Iris Boxplot") +
  stat_summary(fun.y=mean, geom="point", shape=5, size=4) 
```



